Supplement to: Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-10-20 synthesizerOutputs.tex
new writing on learning to synthesize and a new program features PCA result

        \begin{minipage}{10cm}
        \begin{verbatim}
line(6,2,6,3,
arrow = False,solid = True);
line(6,2,3,2,
arrow = True,solid = True);
reflect(reflect(y = 9)){
line(3,2,5,4,
arrow = True,solid = True);
rectangle(0,0,8,9);
rectangle(5,3,7,6);
rectangle(1,1,3,3)
}
        \end{verbatim}
\end{minipage}

@@

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(4,2,6,5);
reflect(reflect(y = 7)){
line(2,6,4,4,
arrow = True,solid = True);
rectangle(0,0,2,2)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(10,5);
line(7,5,9,5,
arrow = True,solid = True);
rectangle(5,3,7,7);
rectangle(0,0,12,10);
reflect(reflect(y = 10)){
line(3,8,5,6,
arrow = True,solid = True);
rectangle(1,7,3,9)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(10,4);
line(10,1,2,1,
arrow = True,solid = False);
line(10,1,10,3,
arrow = False,solid = False);
line(7,4,9,4,
arrow = True,solid = True);
reflect(reflect(y = 8)){
line(2,7,4,5,
arrow = True,solid = True);
rectangle(4,2,7,6);
rectangle(0,6,2,8)
}
        \end{verbatim}
\end{minipage}

@@

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,1,2,0,
arrow = False,solid = True);
for (i < 3){
if (i > 0){
line(3*i + -3,4,3*i + -1,3,
arrow = False,solid = True);
line(0,3*i + -2,3*i + -3,4,
arrow = False,solid = True)
}
rectangle(2,0,5,3)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
circle(-3*i + 7,1);
circle(-3*i + 7,6);
line(-3*i + 7,-1*i + 4,-3*i + 7,5,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(2,6,5,6,
arrow = False,solid = True);
reflect(reflect(x = 7)){
circle(6,1);
line(2,1,5,1,
arrow = False,solid = True);
line(1,2,1,5,
arrow = False,solid = True);
rectangle(5,5,7,7)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(2,1,4,1,
arrow = True,solid = True);
line(3,2,1,2,
arrow = True,solid = True);
line(5,0,3,0,
arrow = True,solid = True);
line(0,3,2,3,
arrow = True,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 4){
if (i > 0){
rectangle(-2*i + 6,2*i + -2,-2*i + 7,2*i + -1)
}
rectangle(-2*i + 6,2*i,-2*i + 7,2*i + 1)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,3,2,3,
arrow = False,solid = False);
line(2,1,4,1,
arrow = False,solid = False);
line(1,2,3,2,
arrow = False,solid = True);
line(3,0,5,0,
arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 4){
if (i > 0){
circle(-2*i + 7,3*i + -2);
line(-2*i + 9,3*i,-2*i + 10,3*i + -2,
arrow = False,solid = True);
line(-2*i + 8,3*i + -2,-2*i + 9,3*i,
arrow = False,solid = True)
}
circle(-2*i + 9,3*i + 1)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 4){
if (i > 0){
line(2*i + 1,-3*i + 12,2*i,-3*i + 10,
arrow = True,solid = True);
line(2*i + 1,-3*i + 12,2*i + 2,-3*i + 10,
arrow = True,solid = True);
rectangle(2*i + -2,-3*i + 9,2*i,-3*i + 11)
}
rectangle(2*i + 2,-3*i + 9,2*i + 4,-3*i + 11)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(5,1);
for (i < 3){
if (i > 0){
circle(7,2*i + -1);
circle(i + 2,2*i + 1)
}
circle(1,6)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(4,4,2,2,
arrow = True,solid = True);
rectangle(3,4,5,6);
rectangle(0,0,2,2)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(0,4,2,6);
for (i < 3){
if (i > 0){
line(-4*i + 12,5,-4*i + 10,5,
arrow = True,solid = True);
for (j < i + 1){
circle(-4*j + 9,-4*i + 9)
}
}
line(-4*i + 9,4,-4*i + 9,2,
arrow = True,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(-4*i + 9,4,-4*i + 9,2,
arrow = True,solid = True);
for (j < 2){
line(-4*j + 8,5,-4*j + 6,5,
arrow = True,solid = True);
rectangle(-4*i + 8,4*j,-4*i + 10,4*j + 2)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
line(-4*i + 12,1,-4*i + 10,1,
arrow = True,solid = True)
}
circle(-4*i + 9,1);
circle(-4*i + 9,5);
line(-4*i + 9,2,-4*i + 9,4,
arrow = True,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 6)){
for (i < 3){
if (i > 0){
line(-2*i + 7,-4*i + 11,-2*i + 7,-4*i + 10,
arrow = True,solid = True);
rectangle(0,-4*i + 11,6,-3*i + 12)
}
rectangle(2,0,4,2)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
line(3*i,1,3*i + -1,1,
arrow = True,solid = True)
}
rectangle(3*i,0,3*i + 2,2)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(1,3,1,4,
arrow = False,solid = True);
for (i < 3){
if (i > 0){
line(1,-5*i + 13,1,-4*i + 10,
arrow = True,solid = True)
}
circle(1,-4*i + 9)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 2)){
line(0,1,1,2,
arrow = False,solid = True);
line(1,0,2,1,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(i,-1*i + 6,2*i + 2,-1*i + 6,
arrow = False,solid = True);
line(i,-2*i + 4,i,-1*i + 6,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
circle(1,-3*i + 7);
circle(5,-2*i + 6);
rectangle(0,-3*i + 6,2,-3*i + 8)
}
rectangle(4,1,6,5)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
rectangle(3*i,-2*i + 4,3*i + 2,6);
for (j < i + 1){
circle(3*i + 1,-2*j + 5)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,0,6,0,
arrow = False,solid = False);
reflect(reflect(x = 6)){
line(6,0,6,3,
arrow = False,solid = True);
line(0,3,6,3,
arrow = False,solid = False)
}
        \end{verbatim}
\end{minipage}

@@

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
circle(-5*i + 11,1);
line(-1*i + 3,-1*i + 7,-5*i + 11,2,
arrow = True,solid = True)
}
circle(1,6)
}
        \end{verbatim}
\end{minipage}

@@

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
line(4*i + -3,-5*i + 12,2*i + 1,5,
arrow = False,solid = True);
rectangle(4*i + -4,-5*i + 10,6,-7*i + 16)
}
circle(1,8)
}
        \end{verbatim}
\end{minipage}

@@

@@

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
circle(-3*i + 7,1)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
rectangle(-2*i + 4,0,-2*i + 5,6)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(4,0,4,5,
arrow = False,solid = True);
line(0,0,0,5,
arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 12)){
circle(4,1);
line(9,1,10,1,
arrow = False,solid = True);
rectangle(0,0,2,2)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(0,4,4,8);
reflect(reflect(y = 12)){
circle(7,6);
line(2,2,2,4,
arrow = True,solid = True);
line(4,6,6,6,
arrow = True,solid = True);
rectangle(1,10,3,12)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(y = 9)){
line(3,8,6,8,
arrow = False,solid = True);
reflect(reflect(x = 9)){
circle(1,8);
line(1,3,1,6,
arrow = False,solid = True)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(y = 11)){
rectangle(4,9,7,10);
reflect(reflect(x = 11)){
rectangle(1,4,2,7);
rectangle(8,8,11,11)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 4){
line(i,-1*i + 5,i + 2,-1*i + 5,
arrow = False,solid = True);
line(i + 2,-1*i + 3,i + 4,-1*i + 3,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
rectangle(3*i + 1,-1*i + 2,3*i + 3,2);
rectangle(0,7*i + -7,3,7*i + -4)
}
rectangle(1,4,2,6)
}
        \end{verbatim}
\end{minipage}

@@

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
rectangle(-2*i + 4,-2*i + 4,-2*i + 7,-2*i + 5)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(4,10);
for (i < 3){
circle(-3*i + 7,5);
circle(-3*i + 7,1);
line(-3*i + 7,4,-3*i + 7,2,
arrow = True,solid = True);
line(4,9,-3*i + 7,6,
arrow = True,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(2,8,2,6,
arrow = True,solid = True);
line(6,8,6,4,
arrow = True,solid = True);
line(4,8,4,0,
arrow = True,solid = True);
line(0,8,8,8,
arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(2,3,2,5,
arrow = False,solid = True);
rectangle(1,1,3,3);
rectangle(1,5,3,7);
rectangle(0,0,4,8)
        \end{verbatim}
\end{minipage}

@@

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
for (j < 3){
circle(-4*j + 9,-3*i + 7)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
line(8,0,8*i + -8,7*i + -7,
arrow = True,solid = True)
}
rectangle(2*i + 2,0,2*i + 3,i + 3)
}
        \end{verbatim}
\end{minipage}

@@

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(5,0,8,3);
rectangle(2,1,4,3);
rectangle(0,2,1,3)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
rectangle(-1*i + 2,-1*i + 2,i + 3,i + 3)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 6)){
line(5,2,5,4,
arrow = False,solid = True);
reflect(reflect(y = 6)){
line(2,1,4,1,
arrow = False,solid = True);
rectangle(4,4,6,6)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(y = 6)){
line(2,5,4,5,
arrow = False,solid = True);
reflect(reflect(x = 6)){
circle(5,5);
line(1,2,1,4,
arrow = False,solid = True)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(i,-1*i + 2,-1*i + 7,-1*i + 2,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(1,4,5,0,
arrow = False,solid = True);
line(1,5,5,1,
arrow = False,solid = True);
rectangle(5,0,6,1);
rectangle(0,4,1,5)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
circle(4*i + 1,1);
rectangle(4*i,0,4*i + 2,2)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 5)){
circle(1,1);
line(4,4,4,2,
arrow = True,solid = True);
rectangle(0,4,5,6)
}
        \end{verbatim}
\end{minipage}

>>>>

        \begin{minipage}{10cm}
        \begin{verbatim}
line(6,2,6,3,
arrow = False,solid = True);
line(6,2,3,2,
arrow = True,solid = True);
reflect(y = 9){
line(3,7,5,5,
arrow = True,solid = True);
rectangle(1,1,3,3);
rectangle(5,3,7,6);
rectangle(0,0,8,9)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 2){
line(8,8,3,8,
arrow = True,solid = False);
line(-2 * i + 12,5,-2 * i + 13,5,
arrow = True,solid = True);
line(6,5,7,5,
arrow = True,solid = True);
line(3,-6 * i + 8,5,-2 * i + 6,
arrow = True,solid = True);
rectangle(-2 * i + 13,4,-2 * i + 14,6);
rectangle(1,-6 * i + 7,3,-6 * i + 9)
};
circle(8,5);
rectangle(5,3,6,7);
rectangle(0,0,10,10);
line(8,6,8,8,
arrow = False,solid = False)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(y = 7){
line(2,6,4,4,
arrow = True,solid = True);
rectangle(0,0,2,2)
};
rectangle(4,2,6,5)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(7,5,9,5,
arrow = True,solid = True);
rectangle(5,3,7,7);
rectangle(0,0,12,10);
reflect(y = 10){
circle(10,5);
line(3,2,5,4,
arrow = True,solid = True);
rectangle(1,1,3,3)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(10,1,2,1,
arrow = True,solid = False);
line(10,1,10,3,
arrow = False,solid = False);
line(7,4,9,4,
arrow = True,solid = True);
reflect(y = 8){
circle(10,4);
line(2,1,4,3,
arrow = True,solid = True);
rectangle(4,2,7,6);
rectangle(0,6,2,8)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(12,9,12,0,
arrow = True,solid = True);
rectangle(9,3,11,9);
rectangle(6,5,8,9);
rectangle(0,7,2,9);
rectangle(3,8,5,9)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
for (j < (1*i + 1)){
if (j > 0){
line(3 * j + -3,3 * i + -2,3 * j + -1,3 * i + -3,
arrow = False,solid = True);
line(0,3 * j + -2,3 * j + -3,4,
arrow = False,solid = True)
}
rectangle(2,0,5,3)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
circle(-3 * i + 7,1);
circle(-3 * i + 7,6);
line(-3 * i + 7,-1 * i + 4,-3 * i + 7,5,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(x = 7){
circle(6,1);
line(6,2,6,5,
arrow = False,solid = True);
rectangle(5,5,7,7)
};
line(2,6,5,6,
arrow = False,solid = True);
line(2,1,5,1,
arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(3,2,1,2,
arrow = True,solid = True);
line(0,3,2,3,
arrow = True,solid = True);
line(5,0,3,0,
arrow = True,solid = True);
line(2,1,4,1,
arrow = True,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(6,0,7,1);
for (i < 3){
rectangle(-2 * i + 4,2 * i + 2,-2 * i + 5,2 * i + 3);
rectangle(-2 * i + 4,2 * i,-2 * i + 5,2 * i + 1)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(3,0,5,0,
arrow = False,solid = True);
line(1,2,3,2,
arrow = False,solid = True);
line(0,3,2,3,
arrow = False,solid = False);
line(2,1,4,1,
arrow = False,solid = False)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(9,1);
for (i < 3){
circle(-2 * i + 7,3 * i + 4);
circle(-2 * i + 5,3 * i + 1);
line(-2 * i + 6,3 * i + 1,-2 * i + 7,3 * i + 3,
arrow = False,solid = True);
line(-2 * i + 7,3 * i + 3,-2 * i + 8,3 * i + 1,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(2 * i + 3,-3 * i + 9,2 * i + 2,-3 * i + 7,
arrow = True,solid = True);
line(2 * i + 3,-3 * i + 9,2 * i + 4,-3 * i + 7,
arrow = True,solid = True);
rectangle(2 * i + 2,-3 * i + 9,2 * i + 4,-3 * i + 11);
rectangle(2 * i,-3 * i + 6,2 * i + 2,-3 * i + 8)
};
rectangle(8,0,10,2)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 2){
circle(2 * i + 1,-3 * i + 6);
circle(-3 * i + 7,2 * i + 3);
circle(2 * i + 5,1)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(4,4,2,2,
arrow = True,solid = True);
rectangle(0,0,2,2);
rectangle(3,4,5,6)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(-4 * i + 9,4,-4 * i + 9,2,
arrow = True,solid = True);
for (j < (1*i + 2)){
if (j > 0){
circle(-4 * j + 13,-4 * i + 9);
line(-4 * i + 12,5,-4 * i + 10,5,
arrow = True,solid = True)
}
rectangle(0,4,2,6)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(1,5);
line(4,1,2,1,
arrow = True,solid = True);
line(8,1,6,1,
arrow = True,solid = True);
for (i < 3){
line(4 * i + 1,2,4 * i + 1,4,
arrow = True,solid = True);
rectangle(4,4,6,6);
rectangle(4 * i,0,4 * i + 2,2)
};
rectangle(8,4,10,6)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(4 * i + 1,4,4 * i + 1,2,
arrow = True,solid = True);
for (j < 2){
line(4 * j + 4,5,4 * j + 2,5,
arrow = True,solid = True);
rectangle(4 * i,-4 * j + 4,4 * i + 2,-4 * j + 6)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(4 * i + 1,2,4 * i + 1,4,
arrow = True,solid = True);
for (j < 2){
circle(4 * i + 1,4 * j + 1);
line(4 * j + 4,1,4 * j + 2,1,
arrow = True,solid = True)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(5,7,5,6,
arrow = True,solid = True);
line(3,3,3,2,
arrow = True,solid = True);
line(1,7,1,6,
arrow = True,solid = True);
rectangle(0,3,6,6);
rectangle(2,0,4,2);
rectangle(0,7,6,9)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(6,1,5,1,
arrow = True,solid = True);
for (i < 3){
line(3,1,2,1,
arrow = True,solid = True);
rectangle(3 * i,0,3 * i + 2,2)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
circle(1,-4 * i + 9)
};
line(1,4,1,2,
arrow = True,solid = True);
line(1,8,1,6,
arrow = True,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(y = 2){
line(0,1,1,2,
arrow = False,solid = True);
line(1,0,2,1,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(1 * i,-2 * i + 4,1 * i,-1 * i + 6,
arrow = False,solid = True);
line(1 * i,-1 * i + 6,2 * i + 2,-1 * i + 6,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(5,2);
circle(5,4);
rectangle(4,1,6,5);
reflect(y = 5){
circle(1,4);
rectangle(0,3,2,5)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
for (j < (1*i + 1)){
circle(3 * i + 1,-2 * j + 5)
};
rectangle(3 * i,-2 * i + 4,3 * i + 2,6)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,0,0,3,
arrow = False,solid = True);
line(6,0,6,3,
arrow = False,solid = True);
line(0,3,6,3,
arrow = False,solid = False);
line(0,0,6,0,
arrow = False,solid = False)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 2){
line(2 * i,-2 * i + 5,2,5,
arrow = False,solid = True);
line(1,2,2 * i + 1,-2 * i + 4,
arrow = False,solid = True);
line(2 * i + 3,-2 * i + 3,5,3,
arrow = False,solid = True);
line(4,0,2 * i + 4,-2 * i + 2,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(6,1);
circle(1,1);
circle(1,6);
line(2,6,6,2,
arrow = True,solid = True);
line(1,5,1,2,
arrow = True,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(5,5,9,9);
rectangle(0,0,4,4);
for (i < 2){
rectangle(1 * i + 7,-2 * i + 2,9,-3 * i + 4);
rectangle(0,-3 * i + 8,1 * i + 1,-2 * i + 9)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(1,8);
line(5,2,5,5,
arrow = False,solid = True);
line(1,7,3,5,
arrow = False,solid = True);
rectangle(4,0,6,2);
rectangle(0,5,6,9)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
for (j < 3){
if (j > 0){
line(3 * j + -1,3 * i + 1,3 * j,3 * i + 1,
arrow = False,solid = True);
line(3 * i + 1,3 * j + -1,3 * i + 1,3 * j,
arrow = False,solid = True)
}
circle(3 * i + 1,3 * j + 1)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
for (j < 3){
if (j > 0){
line(3 * i + 1,3 * j + -1,3 * i + 1,3 * j,
arrow = False,solid = True);
line(3 * j + -1,3 * i + 1,3 * j,3 * i + 1,
arrow = False,solid = True)
}
rectangle(3 * i,3 * j,3 * i + 2,3 * j + 2)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
circle(-3 * i + 7,1)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
rectangle(-2 * i + 4,0,-2 * i + 5,6)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,0,0,5,
arrow = False,solid = True);
line(4,0,4,5,
arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(x = 12){
circle(4,1);
line(2,1,3,1,
arrow = False,solid = True);
rectangle(0,0,2,2)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(7,6);
reflect(y = 12){
line(4,6,6,6,
arrow = True,solid = True);
line(2,10,2,8,
arrow = True,solid = True);
rectangle(1,0,3,2)
};
rectangle(0,4,4,8)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(y = 9){
reflect(x = 9){
circle(8,8);
line(3,8,6,8,
arrow = False,solid = True);
line(1,3,1,6,
arrow = False,solid = True)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(x = 11){
rectangle(9,4,10,7);
reflect(y = 11){
rectangle(8,0,11,3);
rectangle(4,9,7,10)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(2 * i,-2 * i + 5,2 * i + 2,-2 * i + 5,
arrow = False,solid = True);
line(2 * i + 1,-2 * i + 4,2 * i + 3,-2 * i + 4,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(4,1,6,2);
rectangle(7,0,9,2);
reflect(y = 10){
rectangle(0,0,3,3);
rectangle(1,4,2,6)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(7,4,9,4,
arrow = True,solid = True);
line(8,3,7,3,
arrow = True,solid = True);
reflect(y = 7){
line(2,1,4,3,
arrow = True,solid = True);
rectangle(0,0,2,2)
};
line(8,3,9,3,
arrow = False,solid = True);
rectangle(9,2,12,5);
rectangle(4,2,7,5)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
rectangle(2 * i,2 * i,2 * i + 3,2 * i + 1)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(4,10);
for (i < 3){
circle(3 * i + 1,1);
circle(3 * i + 1,5);
line(4,9,3 * i + 1,6,
arrow = True,solid = True);
line(3 * i + 1,4,3 * i + 1,2,
arrow = True,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(2,8,2,6,
arrow = True,solid = True);
line(4,8,4,0,
arrow = True,solid = True);
line(6,8,6,4,
arrow = True,solid = True);
line(0,8,8,8,
arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(2,3,2,5,
arrow = False,solid = True);
rectangle(0,0,4,8);
rectangle(1,1,3,3);
rectangle(1,5,3,7)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(0,0,6,2);
reflect(x = 6){
for (i < 3){
circle(5,2 * i + 4);
circle(2 * i + 1,1);
rectangle(4,3,6,9)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
for (j < 3){
circle(4 * i + 1,-3 * j + 7)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(8,0,0,0,
arrow = True,solid = True);
line(8,0,8,7,
arrow = True,solid = True);
for (i < 3){
rectangle(-2 * i + 6,0,-2 * i + 7,-1 * i + 5)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(2,4,4,4,
arrow = True,solid = True);
line(6,7,5,5,
arrow = True,solid = True);
for (i < 2){
circle(-2 * i + 7,-3 * i + 7);
circle(3 * i + 4,1);
line(5,3,3 * i + 4,2,
arrow = True,solid = True);
rectangle(0,3,2,5)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(5,0,8,3);
rectangle(0,2,1,3);
rectangle(2,1,4,3)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
rectangle(-1 * i + 2,-1 * i + 2,1 * i + 3,1 * i + 3)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(y = 6){
line(2,5,4,5,
arrow = False,solid = True);
reflect(x = 6){
line(5,2,5,4,
arrow = False,solid = True);
rectangle(0,4,2,6)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(y = 6){
reflect(x = 6){
circle(1,1);
line(5,2,5,4,
arrow = False,solid = True)
};
line(2,1,4,1,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(1 * i,-1 * i + 2,-1 * i + 7,-1 * i + 2,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(1,5,5,1,
arrow = False,solid = True);
line(1,4,5,0,
arrow = False,solid = True);
rectangle(0,4,1,5);
rectangle(5,0,6,1)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
circle(-4 * i + 9,1);
rectangle(-4 * i + 8,0,-4 * i + 10,2)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(x = 5){
circle(4,1);
line(4,4,4,2,
arrow = True,solid = True)
};
rectangle(0,4,5,6)
        \end{verbatim}
\end{minipage}
